Leveraging Collaboration: A Methodology for the Design of Social Problem-Solving Systems

### 2013-01-25 Article.tex
Fiz mais umas modificações sugeridas e incluí os gráficos 3d novos feitos no GNU plot

\title{Social Computing Article\thanks{This title is temporary}}

@@

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in diverse sets of environments. Nevertheless, if not well designed, social and human computation systems may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy or mimic is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
%--Make more specific
In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
%--
That behaviour is referred to as an evidence of conformism in human subjects. On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although %Unfortunately?
an in-depth analysis of that fact was not reported. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons for that in the \emph{Results} section. %We also analyse possible reasons for that behaviour in the \emph{Results} section.

@@

%--Keep?
We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
%--
It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT. Through that process, we compared the problem-solving strategy %strategy?
typically used by humans with alternative, artificial strategies and reached the conclusion that it is detrimental to the problem-solving process.
%--Explain better
We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy.
%--
In addition, we analyse the impact that copying and guessing have on the process of solving the problem. After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.

\section{A Novel Method for %Artificial?
Social Problem Solving}
%P.S. method has two phases: communication and reasoning

@@

We propose a method for solving computational problems by means of a network of agents endowed with social behaviour. Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents. Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}. %cite social psych

\begin{algorithm}
 \SetAlgoLined
 Initialize N agents, each encoding a partial solution to the problem\;
 \While{termination condition not met}
 {
 	\For{i = 1 to N}
 	{
 		\For{j = 1 to N}
 		{
 			\If{j is connected to i}
 			{
 				$A_{i}$ = $i_{th}$ agent\;
 				$A_{j}$ = $j_{th}$ agent\;
 				Add $A_{j}$'s solution to the collection of messages received by $A_{i}$\; %A.messages.add(j.solution)\;
 			}
 		}
 	}
 	\For{i = 1 to N} 
 	{
 		\CommentSty{ //Social Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		selectedMessage = select($A_{i}$.messages)\;

 		\If{random(0,1) $<$ copyRate}
 		{
 			$A_{i}$.solution = selectedMessage\;
 		}
 	}
 	\For{i = 1 to N}
 	{
 		\CommentSty{ //Cognitive Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		Add local changes to $A_{i}$'s solution%$A_{i}$.solution = addLocalChanges($A_{i}$.solution)\;
 	}
 }
 \caption{Algorithm for the proposed model, encompassing the social and cognitive stages}
\end{algorithm}

\begin{itemize}
\item
Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections. Agents are thus presented with a multiplicity of messages. There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions. We call this probability the {\em Copy Rate}. When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages. This is done by means of a particular message-selecting strategy.

\item
Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
\end{itemize}

%--Change focus
\section{Performance Tests}
%--

@@

\subsection{Social Stage} %Generalize!

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion. We have modelled three message-selecting strategies to employ in the \emph{Social Stage}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.

\subsubsection{{\em Pick Most Filled} strategy}

@@

\subsubsection{{\em Pick Among First} strategy}

@@

\subsubsection{{\em Pick Random} strategy}

@@

\subsection{Cognitive Stage}

{\em Sudoku} solving techniques are abundant in literature. %{\em Sudoku} strategy literature?
Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles. Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.

@@

\subsection{Copying Solutions}

@@

We incorporated this copying frequency into our modelling, recreating the scenario of the experiments conducted by~\cite{farenzena:collabem} by setting this parameter accordingly to the topologies we used.

@@

\section{Results and Analysis}

@@

We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network. Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the cognitive and social stages. That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}. Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the cognitive stage and the metric employed to pick a neighbour to copy, into the social stage.

@@

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_most}
\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric). The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
}
\label{fig:copy_guess_free_most}
\end{figure}

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_prob}
\caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob}
\end{figure}

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob_num_solution_reached}
\end{figure}

@@

The results also differ depending on the copying strategy employed in the \emph{social stage}. It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions. The graph in Figure~\ref{fig:copy_guess_free_most} shows that as copying increases, the number of rounds necessary for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level. Meanwhile, the benefits of guessing are much less pronounced. On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Figure~\ref{fig:copy_guess_free_prob}, their contributions don't differ as much. Those results confirm that the worth of copying increases when the proposed solutions are evaluated.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly. Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.

>>>>

\title{Leveraging Collaboration: 
A Methodology for the Design of Social Problem-Solving Systems}

@@

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in diverse sets of environments. 
Nevertheless, if not well designed, social and human computation systems may achieve results 
only similar to those of a single human subject performing a task. 
This scenario reflects a need for better understanding of the performance 
issues of human problem-solving social networks. 
We carry out several experiments on artificial social problem-solving 
supported by results of experiments carried out with human subjects, 
in order to analyse which parameters influence the performance of collaborative problem-solving social networks. 
We analyse the strategies humans follow when solving a problem, 
comparing them with alternative strategies, and 
identify the consequences of the employed strategies 
in the collective performance of the social network.
Our results also indicate that copying and guessing are highly beneficial to the 
performance of the social networks. 
We then propose mechanisms that can improve human problem-solving abilities.
Finally, we show that our results lead to a methodology for the design  
of efficient problem-solving systems that can be applied 
to several kinds of collaborative social systems. 
\end{abstract}

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
%--Make more specific
In that study a specific pattern of behaviour was observed which suggests that humans didn't evaluate the solutions proposed by their neighbours, instead choosing to copy the solutions which were displayed closer in the system's interface.
%--Done
That behaviour is referred to as an evidence of conformism in human subjects. On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although %Unfortunately?
an in-depth analysis of that fact was not reported. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons for that in section~\ref{sec:results}. %We also analyse possible reasons for that behaviour in the \emph{Results} section.

@@

We have developed a novel method for artificial social problem-solving that can be used to simulate the behaviour observed in humans in collective problem-solving systems. This model is described on section~\ref{sec:model}.

The methodology was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We describe how we adapted that environment and the behaviour of its subjects to our system in section~\ref{sec:apply}. We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT. However, the results obtained can be generalized to different problems.

In the experiments performed by~\cite{farenzena:collabem}, it was verified that the human subjects didn't evaluate their neighbours' solutions, instead choosing an arbitrary solution based on position in the interface. We simulated that behaviour in our agents and compared that strategy with alternative, artificial strategies, and reached the conclusion that the human strategy is detrimental to the problem-solving process. A network of agents that evaluated the solutions proposed to them performed consistently better, even though the evaluation function employed wasn't one that accurately represented the solution's worth. That way, we verify that even a naive evaluation tactic surpasses choosing an arbitrary neighbour to copy. A more detailed analysis is provided in section~\ref{sec:results}.

In addition, we analyse the impact that copying and guessing have on the process of solving the problem. After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.

\section{A Novel Method for %Artificial?
Social Problem Solving}
\label{sec:model}
%P.S. method has two phases: communication and reasoning

@@

We propose a method for solving computational problems by means of a network of agents endowed with social behaviour. Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents. Additionally, our algorithm is composed of two stages, namely the {\em communication phase} and the {\em reasoning phase}. %cite social psych

\begin{algorithm}
 \SetAlgoLined
 Initialize N agents, each encoding a partial solution to the problem\;
 \While{termination condition not met}
 {
 	\For{i = 1 to N}
 	{
 		\For{j = 1 to N}
 		{
 			\If{j is connected to i}
 			{
 				$A_{i}$ = $i_{th}$ agent\;
 				$A_{j}$ = $j_{th}$ agent\;
 				Add $A_{j}$'s solution to the collection of messages received by $A_{i}$\; %A.messages.add(j.solution)\;
 			}
 		}
 	}
 	\For{i = 1 to N} 
 	{
 		\CommentSty{ //Communication Phase }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		selectedMessage = select($A_{i}$.messages)\;

 		\If{random(0,1) $<$ copyRate}
 		{
 			$A_{i}$.solution = selectedMessage\;
 		}
 	}
 	\For{i = 1 to N}
 	{
 		\CommentSty{ //Reasoning Phase }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		Add local changes to $A_{i}$'s solution%$A_{i}$.solution = addLocalChanges($A_{i}$.solution)\;
 	}
 }
 \caption{Algorithm for the proposed model, encompassing the communication and reasoning phases}
\end{algorithm}

\begin{itemize}
\item
Communication phase: In the {\em communication phase}, messages are passed from agent to agent through the network connections. Agents are thus presented with a multiplicity of messages. There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions. We call this probability the {\em Copy Rate}. When an agent chooses to copy, it is then supposed to select for copying a single one of its received messages. This is done by means of a particular message-selecting strategy.

\item
Reasoning phase: In the {\em reasoning phase}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
\end{itemize}

%--Change focus
\section{Performance Tests}
\label{sec:apply}
%--

@@

\subsection{Communication Phase} %Generalize!

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors' analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion. We have modelled three message-selecting strategies to employ in the \emph{communication phase}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.

\subsubsection{{\em Most Filled} strategy}

@@

%This is not an accurate measurement of fitness

\subsubsection{{\em First Positions} strategy}

@@

\subsubsection{{\em Random} strategy}

@@

Although used here in the context of the \emph{Sudoku} problem, these strategies can be generalized to apply to different problems. It was verified in~\cite{farenzena:collabem} that the human behaviour of copying arbitrary solutions was not strictly dependent on the problem, since similar results were obtained for both SAT and \emph{Sudoku}. Meanwhile, the \emph{Most Filled} strategy can be adapted appropriately to the relevant problem. For example, in solving the SAT problem one can evaluate solutions by counting the number of clauses that evaluate to \emph{true}.

\subsection{Reasoning Phase}

The techniques employed by the agents to advance the solution individually should be chosen according to the problem in question. In the case of {\em Sudoku}, solving techniques are abundant in literature. %{\em Sudoku} strategy literature?
Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles. Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em reasoning phase} to add local changes to the {\em Sudoku} message received in the {\em communication phase}.

@@

%--Keep?
\subsection{Copying Solutions}

@@

We incorporated this copying frequency into our modelling, recreating the scenario of the experiments conducted by~\cite{farenzena:collabem} by setting this parameter accordingly to the topologies we used.
%--

@@

\section{Results and Analysis}
\label{sec:results}

@@

We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network. Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the reasoning and communication phases. That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}. Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the reasoning phase and the metric employed to pick a neighbour to copy, into the communication phase.

@@

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/fill_iter}
\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric). The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
}
\label{fig:copy_guess_free_most}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/fill_suc}
\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick most filled' selection metric).
}
\label{fig:copy_guess_free_most}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/first_iter}
\caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/first_suc}
\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob_num_solution_reached}
\end{figure}

@@

The results also differ depending on the copying strategy employed in the \emph{communication phase}. It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions. The graph in Figure~\ref{fig:copy_guess_free_most} shows that as copying increases, the number of rounds necessary for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level. Meanwhile, the benefits of guessing are much less pronounced. On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Figure~\ref{fig:copy_guess_free_prob}, their contributions don't differ as much. Those results confirm that the worth of copying increases when the proposed solutions are evaluated.

@@

Of the three metrics employed by us in the \emph{communication phase}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly. Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.
